### 2022-11-01 Papers/ICCC-2023/sections/implementation.tex
aproximatley finished implementation section

Figure \ref{fig:interpreter_data_structures} contains a class diagram of most of the types used to represent values within C-=-1.
All of them derive from \lstinline{IRuntimeValue} and are managed via C++ smart pointers.
The interface of the base class allows the value to be converted to a human-readable format, serialisation, deserialisation and copying.

@@

Functions \lstinline{buildFunction} and \lstinline{getFunctionName}, from Listing \ref{lst:selected_backend_interface}, are parts of Backend Interface.
They are invoked in order to convert a C-=-1 \lstinline{functionDescriptor} to a LLVMIR function.
They were included in the Listing, because they are the only parts of the Backend Intreface that need to interact with \lstinline{ISymbolNameOverride} attributes.

>>>>

Figure \ref{fig:interpreter_data_structures} contains a class diagram of most of the types used to represent values within C-=-1.
All of them derive from \lstinline{IRuntimeValue} and are managed via C++ smart pointers.
The interface of the base class allows the value to be converted to a human-readable format, serialization, deserialization and copying.

@@

Functions \lstinline{buildFunction} and \lstinline{getFunctionName}, from Listing \ref{lst:selected_backend_interface}, are parts of Backend Interface.
They are invoked in order to convert a C-=-1 \lstinline{functionDescriptor} to a LLVMIR function.
They were included in the Listing, because they are the only parts of the Backend Intreface that need to interact with \lstinline{ISymbolNameOverride} attributes.
Both of these procedures, check whether an attribute implementing this interface is attached to the function they are currently processing.
This happens on lines three and nineteen of Listing \ref{lst:selected_backend_interface}.
If that attribute is present, code of that function is ignored, and it is treated as an external symbol: condition on line twenty ommits execution of \lstinline{build_block} function on line twenty-three.
Procedure \lstinline{getFunctionName} contains a similar condition on line three, that decides how the name should be generated.
If an \lstinline{ISymbolNameOverride} attribute is present, it will be created by \lstinline{createSymbolName} method of the attribute attached to the function.
Otherwise, the \lstinline{mangleName} function will create name of function's symbol based on its parameters and return type.
